%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Career Related Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Science Immersive Fellow} % Job title
    {General Assembly} % Organization
    {Boston, MA} % Location
    {Apr. 2018 - Jul 2018} % Date(s)
    {During this full-time intensive Data Science program, my job is to master the art of taking large data sets and analyze them using different types of models and algorithms to gain insights and predict trends.}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed visual and statistical analysis on 60 + real world datasets using Python and its associated libraries and tools}
        \item {Performed visual and statistical analysis on data using Python and its associated libraries and tools}
        \item {Built, implemented, and evaluated data science problems using appropriate machine learning models and algorithms, ranging from simple Linear Regression to CARTS and LSTMs.}
        \item {Used appropriate data visualizations to communicate findings and create clear and reproducible reports to stakeholders.}
        \item {Learned to identify big data problems and articulate how distributed systems and parallel computing technologies (i.e AWS, Databricks) are solving these challenges.}
        \item {Applied question, modeling, and validation problem-solving processes to datasets from various industries to provide insight into real-world problems and solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Digital Marketing Specialist} % Job title
    {Flatbook (now Sonder)} % Organization
    {Montreal, QC} % Location
    {Mar. 2015 - Nov. 2016} % Date(s)
    {Sonder brings hotel hospitality to the sharing economy. Clients can rent one-of-a-kind Sonders in unique neighborhoods and find the same consistent standard of quality inside: crisp white linens, high-end kitchen and bath essentials, and 24/7 concierge service.}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed digital marketing strategies (paid, earned and organic media) for projects, including the company website and social media, while also pursuing alternative marketing channel}
        \item {Created weekly reports for executives and investors by analyzing all online presence data to determine campaign efficiency as per our brand objectives and KPIs}
        \item {Ensured creative marketing materials underwent regular review and adhered to brand guidelines, as well as analyzing all online presence data to determine campaign efficiency as per our brand objectives and KPIs}
        \item {Responsible for maintaining our database and tracking the progress of all leases signed and tenant profiles, ensuring city team CRMs were up to date}
        \item {Coordinated the migration and development of growing client base as we rebranded the company and prepared for our Series A fundraising round}
        \item {Advised UI/UX designers and the creative team on landing page design and copywriting, based on industry best practice}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Development Manager} % Job title
    {Binder Inc.} % Organization
    {Montreal, QC} % Location
    {Sept. 2014 - Mar. 2015} % Date(s)
    {Binder (previously Endeavor Up), is a venture- backed startup that was part of the Founder Fuel 2014 cohort at Notman House. Binder connects top college candidates to employers in a simple, engaging and efficient way. Clients we’ve worked with: Merrill Lynch, KPMG, Saatchi & Saatchi, Ogilvy & Mathers, Ubisoft, and many others}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed and expanded the campus ambassador program, consisting of over 70 student spokespersons on campuses across North America. This helped grow our user base from 300 students to 5,700 in 3 months}
        \item {Conducted weekly calls and meetings with corporate clients and job providers to improve our talent pairing process}
        \item {Managed the internal CRM, using website analytics to refine marketing strategy (measuring against KPIs)}
        \item {Proactively developed new strategic partnerships with organizations like Elite Daily, Intern Queen and Chinese Language Institute}
        \item {Wrote articles and weekly blog posts for the Binder student blog, along with SEO optimization all posts and creative content}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Marketing & Brand Management Assistant} % Job title
    {Cesium Telecom} % Organization
    {Montreal, QC} % Location
    {Jan. 2014 - Nov. 2014} % Date(s)
    {Cesium is one of North America’s leading distributors with over 2,000 distribution points of Original Equipment Manufacturer (OEM) and other branded wireless-related products. It serves various distribution channels, providing the best in consumer electronics}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created professional product presentations, sales sheets, B2B email newsletters via MailChimp, using A/B testing and increased median open rate from 7\% to 43\%}
        \item {Support of website content management; basic graphic design, banner creation, product reviews, all while maintaining both Cesium and supplier’s brand identity throughout.}
        \item {Assisted marketing department in new campaign creation and developing CRM & post-campaign marketing KPI reports for brand/product evaluation.}
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Software Engineer} % Job title
%     {ShitOne Corp.} % Organization
%     {Seoul, S.Korea} % Location
%     {Dec. 2011 - Feb. 2012} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Developed a proxy drive smartphone application which connects proxy driver and customer.}
%         \item {Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
%       \end{cvitems}
%     }
%
% %---------------------------------------------------------
%   \cventry
%     {Freelance Penetration Tester} % Job title
%     {SAMSUNG Electronics} % Organization
%     {S.Korea} % Location
%     {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
%         \item {Conducted penetration testing on SAMSUNG Smart TV.}
%       \end{cvitems}
%       %\begin{cvsubentries}
%       %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
%       %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%       %\end{cvsubentries}
%     }
%
% %---------------------------------------------------------
\end{cventries}
